---
title: "05_run_bootstrap_parallel"
output: github_document
---

This file creates the resamples data from the parallel approach, `results/parallel-bootstrap-resamples.rds`, and a file with summary statistics, `results/parallel-bootstrap-mean-and-ci.rds`

It requires:
* `results/pct_completions.rds`
* `src/R/bootstrap-functions.R`
* `src/R/connect-to-ec2.R`
* `data/ssh_info.csv`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(rsample)
library(ggpubr)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(parallelly)
```

Load data and functions

```{r load-data, message=FALSE, warning =FALSE}
pct_completions <- readRDS(here("results", "pct_completions.rds"))
source(here("src/R", "bootstrap-functions.R"))
source(here("src/R", "connect-to-ec2.R"))
ssh_info <- read_csv(here("data", "ssh_info.csv"))
```

Connect to EC2

```{r}
public_ip <- ssh_info$ip
ssh_private_key_file <- ssh_info$filepath
cl <- connect_to_ec2(public_ip, ssh_private_key_file)
cl
```

Run Bootstrap

```{r cache=TRUE}
plan(cluster, workers = cl)
resamples <- future_get_bootstrap_prop_means(original_dat=pct_completions, ntimes = 100000)
mean(resamples)
sd(resamples)
```

Disconnect EC2

```{r}
plan(sequential)
parallel::stopCluster(cl)
```

Create data frame with observed mean, bootstrap mean, and bootstrap confidence interval

```{r}
obs_mean <- mean(pct_completions$prop)
bootmean <- mean(resamples)
ci <- c("lb"=bootmean-sd(resamples),
        "ub"=bootmean+sd(resamples))

future_means_and_ci <- data.frame(
  obs_mean = obs_mean,
  bootmean  = bootmean,
  "2.5%" = ci[1],
  "97.5%" = ci[2])

rownames(future_means_and_ci) <- NULL
```

Export results

```{r}
saveRDS(resamples, here("results", "parallel-bootstrap-resamples.rds"))
saveRDS(future_means_and_ci, here("results", "parallel-bootstrap-mean-and-ci.rds"))
```
