---
title: Bootstrap 
output: github_document
---


```{r setup, message = FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(rsample)
library(ggpubr)
library(magrittr)
library(purrr)
set.seed(171819)
```

```{r load-data, message=FALSE, warning =FALSE}
pct_completions <- readRDS(here("data", "pcta.rds"))
pct_completions <- pct_completions %>%
  mutate(prop = completions/(northbound+southbound),
         year = factor(year))
```


## Question of interest: What's the average proportion of hikers who complete the Pacific Crest Trail

First, get an idea of the data. 

```{r}
pct_completions %>% 
  ggplot(aes(x = year, y=prop)) +
  geom_point(color = "darkblue") +
  labs(title = "Observed proportions of thru-hikers who completed \nthe Pacific Crest Trail each year",
       caption = "\nNote: Completion of the full 2600 miles is self reported",
       x = "\nYear",
       y = "Proportion of Hikers who Finished \n")+
  theme_light()+
  theme(axis.text.x = element_text(angle=45))
```


```{r}
(obs_mean <- mean(pct_completions$prop))
```

Based on the observed sample I estimate the mean proportion of hikers who finish to be `r obs_mean`.


Now do bootstrap resamples with `bootstraps`

```{r}
resamples <- rsample::bootstraps(pct_completions, times = 10000)
resamples <- resamples %>%
  mutate(mean_prop_completed = map_dbl(splits,~mean(as.data.frame(.)$prop)))
```

Now plot the bootstrap distribution.

```{r}
resamples %>% 
  ggplot(aes(x = mean_prop_completed)) +
    geom_histogram(fill = "darkblue") +
    geom_vline(xintercept = obs_mean) +
    labs(title = "Bootstrap distribution of mean proportion of thru-hikers to \nfinish the Pacific Crest Trail",
      x = "Estimate of Mean Proportion")+
  theme_light()
```

A 95% confidence interval based on percentile method:
```{r}
(ci <- resamples %>% 
  pull(mean_prop_completed) %>% 
  quantile(probs = c(0.025, 0.975)))
```

With 95% confidence the correlation between the income for husbands and wives in opposite gender marriages in Oregon in 2016 is between `r ci[1]` and `r ci[2]`.



